---
title: "Daily Exercise 9 & 10"
author: Nick Beegle
format: html
self-contained: TRUE
editor: visual
---

## Step 1

```{r}
?airquality
```

## Step 2

```{r}
library(visdat)
vis_dat(airquality)
```

The data will need some cleaning because there are missing values for both Ozone and Solar Radiation.

## Step 3

```{r}
cleaned_data <- na.omit(airquality[, c("Ozone", "Wind")])

model <- lm(Ozone ~ Wind, data = cleaned_data)

summary(model)
```

I choose wind because there is no data missing according to the vis_dat graph and wind speed might be associated with the concentration of ozone in the atmosphere.

## Step 4

```{r}
summary(model)
```

I would consider this a valid model because the p-value is less than 0.05 and the R-squared value seems good.

## Step 5

R-squared number represents how well wind explains changes in ozone levels. Say the R-squared value is .6 that means that 60 percent of the variability in ozone can be explained by the variability in wind.

## Step 6

```{r}
library(broom)

augmented_data <- augment(model, cleaned_data)

head(augmented_data)
```

## Step 7

```{r}
library(ggplot2)


ggplot(augmented_data, aes(x = Ozone, y = .fitted)) +
  geom_point() + 
  geom_abline(intercept = 0, slope = 1, color = "red") +  
  labs(
    title = "Actual vs Predicted Ozone",
    subtitle = paste("Correlation:", round(cor(augmented_data$Ozone, augmented_data$.fitted), 2)),
    x = "Actual Ozone",
    y = "Predicted Ozone"
  ) +
  theme_minimal()
```
